Explicit Operations on Parametrised Polytopes

### 2017-01-09 draft.tex
Adapted after merge.
what happened

[ticket: X]
submission to CGTA
Updated and submitted to Computational Geometry: Theory and Applications

\journal{Journal of Combinatorial Theory, Series A}

@@

%% or include affiliations in footnotes:
\author{Rainer M. Schaich\fnref{akn}}
\ead{rainer.schaich@eng.ox.ac.uk}
\fntext[akn]{The author is funded by the EPSRC DTA and the Worcester College Martin Senior Scholarship.}

\author{Mark Cannon}
\ead{mark.cannon@eng.ox.ac.uk}

\address{Department of Engineering Science, University of Oxford, Parks Road, OX1 3PJ, Oxford}

@@

The induced graph~$G(P)$ of a polytope~$P$ is the graph with vertices and edges that coincide with the vertices and edges of the polytope itself~\cite{Bondy:2008}.
%
In this paper we only use one property of induced graphs, namely the \emph{Perles' Conjecture}~\cite{Kalai:1988}:
\emph{For a simple polytope~$P$ the graph~$G(P)$ determines the combinatorial structure of~$P$.}

@@

Since $\mathcal W(p)$ is simple almost everywhere in~$Y$, i.e. each vertex is defined by exactly $n$ active inequalities $\abs{\mathcal A_\kappa(p)}=n$ for all $p\in Y$ and all $\kappa$.

@@

The \emph{Perles' Conjecture}~\cite{Kalai:1988}, states that the combinatorial structure of a simple polytope is uniquely determined by its graph, that is, as long as the induced graph of~$\mathcal W(p)$ remains unchanged so does its combinatorial structure.

@@

Let~$\mathcal C$ be a polyhedral complex such that in each $d$-dimensional element~$\mathcal P_j\in\mathcal C$ the set-valued map is given by $\mathcal W(p) = \{z\in\mathbb R^n:a_i z\leq b_{i,k_j} + c_{i,k_k} p\}$. 
%
It is worth pointing out that any such polyhedral complex is not assumed to be minimal, since the minimal such complex could have non-convex elements, those elements can however be partitioned such that every element of the non-minimal $\mathcal C$ are convex polyhedra. 
%
A natural way to obtain a convex polyhedral complex is by projecting the facets of the set
%
\begin{equation}
  E=\left\{(p,t_1,\dots,t_m)\in Y\times\mathbb R^{m}:\phi_i(p)\leq t_i\right\}
\end{equation}
%
onto $\mathbb R^d$.
%
The set of vertices of elements in the complex coincides with the union of all vertices of $d$-dimensional faces of $\epi(\phi_i)$ for all $i\in\{1,\dots,m\}$, i.e.
%
$$
	\bigcup_{P\in\mathcal C}\text{vert}(P) = \bigcup_{(\ast)} \text{vert}(\pi_d(F)) = \bigcup_{i\in\{1,\dots,m\}}\pi_d(\text{vert}(\epi(\phi_i))),
$$
%
with $(\ast) = \{F: d-\text{dimensional face of } \epi(d_i) \text{ for some } i\in\{1,\dots,m\}\}$.
%
It is now almost obvious that the graph $\mathscr G(\mathcal W\vert_{\mathcal P_j})$ on each $d$-dimensional element $\mathcal P_j\in\mathcal C$ is entirely defined by the values of $\mathcal W(p_j)$ at the vertices $p_j\in\text{vert}(\mathcal P_j)$.
%
In each~$\mathcal P_j$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1,{\bf{0}}\leq\lambda\leq{\bf{1}}\; \forall i\in\{1,\dots,m\}\}$
%
Therefore, if~$\mathcal A_\kappa\subset\{1,\dots,m\}$ such that~$\abs{\mathcal A_\kappa}=d$ and $a_\kappa v_\kappa = t_{\kappa,j}$ defines a vertex for $\mathcal W(p_j)$, then $a_\kappa v_\kappa = \sum_f \lambda_f t_{\kappa,f}$ defines a vertex for $\mathcal W(p)$.

@@

\begin{figure}
\centering
\begin{tikzpicture}[scale=3]
\draw[step=.5,gray,very thin] (-2,-2) grid (2,2);
\foreach \x in {-2,-1.5,...,2} \draw (\x,-2) node[below] {$\x$};
\foreach \y in {-2,-1.5,...,2} \draw (-2,\y) node[left] {$\y$};
\draw[-latex'] (-2,-2) -- (2.2,-2) node[below] {$x_1$};
\draw[-latex'] (-2,-2) -- (-2,2.2) node[left] {$x_2$};
\draw[blue,thick] ( -0.2333,   1.7667) -- ( -1.3333,   0.6667) -- ( -1.4807,   0.5182) -- ( -1.6815,   0.2968) -- ( -1.6720,   0.2560) -- ( -1.6039,   0.1353) -- ( -1.5073,  -0.0145) -- ( -1.0649,  -0.5786) -- ( -0.5663,  -1.1326) -- ( -0.1361,  -1.4875) -- (  0.2333,  -1.7667) -- (  1.3333,  -0.6667) -- (  1.4807,  -0.5182) -- (  1.6499,  -0.3316) -- (  1.5962,  -0.2075) -- (  1.5190,  -0.0928) -- (  1.4796,  -0.0407) -- (  1.1714,   0.3429) -- (  0.9224,   0.6499) -- (  0.1793,   1.4518) -- (  0.1361,   1.4875) -- ( -0.2333,   1.7667) -- cycle;
\draw[red] (  2.0000,   0.0000) -- (  0.0000,   2.0000) -- ( -2.0000,  -0.0000) -- ( -0.0000,  -2.0000) -- (  2.0000,   0.0000) -- cycle;
\foreach \x/\y in { -0.2333/  1.7667,  0.1361/  1.4875,  0.1793/  1.4518, -1.3333/  0.6667, -1.0649/ -0.5786, -1.5073/ -0.0145, -1.6039/  0.1353,  0.9224/  0.6499,  1.6499/ -0.3316,  1.4807/ -0.5182,  1.5962/ -0.2075,  1.4796/ -0.0407,  1.5190/ -0.0928,  1.3333/ -0.6667,  1.1714/  0.3429,  0.2333/ -1.7667, -0.1361/ -1.4875, -0.5663/ -1.1326, -1.6720/  0.2560, -1.6815/  0.2968, -1.4807/  0.5182} \draw[green!80!black] (\x,\y) circle (.75pt);
\foreach \x/\y in {  0.2160/  1.4706,  0.5125/  1.3332,  0.5456/  1.3134, -1.3333/  0.1741, -1.2021/ -0.7778, -1.5526/ -0.4386, -1.6336/ -0.3595,  1.0596/  0.9390,  1.6619/  0.2996,  1.4818/  0.0827,  1.6168/  0.3790,  1.5138/  0.4829,  1.5486/  0.4501,  1.3333/ -0.0915,  1.2515/  0.7356, -0.2160/ -1.3448, -0.5125/ -1.1956, -0.8500/ -1.1326, -1.6915/ -0.3039, -1.6976/ -0.2809, -1.4818/ -0.0094} \draw[yshift=-.5pt,xshift=-.5pt,magenta] (\x,\y) rectangle ++(1pt,1pt);
% \foreach \x/\y in {0.2333/  1.7667,  0.2333/  1.4511, -0.2333/  1.7667, -0.2333/  1.4511,  0.5125/  1.4875,  0.5125/  1.3157,  0.1361/  1.4875,  0.1361/  1.3157,  0.5482/  1.4518,  0.5482/  1.2973,  0.1793/  1.4518,  0.1793/  1.2973, -1.3333/  0.6667, -1.3333/  0.1672, -1.3333/  0.6667, -1.3333/  0.1672, -1.0649/ -0.5786, -1.0649/ -0.7979, -1.2021/ -0.5786, -1.2021/ -0.7979, -1.5073/ -0.0145, -1.5073/ -0.4386, -1.5614/ -0.0145, -1.5614/ -0.4386, -1.6039/  0.1353, -1.6039/ -0.3664, -1.6336/  0.1353, -1.6336/ -0.3664,  1.0596/  0.9404,  1.0596/  0.6499,  0.9224/  0.9404,  0.9224/  0.6499,  1.6684/  0.3316,  1.6684/ -0.3316,  1.6499/  0.3316,  1.6499/ -0.3316,  1.4818/  0.0948,  1.4818/ -0.5182,  1.4807/  0.0948,  1.4807/ -0.5182,  1.6210/  0.3790,  1.6210/ -0.2075,  1.5962/  0.3790,  1.5962/ -0.2075,  1.5171/  0.4829,  1.5171/ -0.0407,  1.4796/  0.4829,  1.4796/ -0.0407,  1.5486/  0.4514,  1.5486/ -0.0928,  1.5190/  0.4514,  1.5190/ -0.0928,  1.3333/ -0.0906,  1.3333/ -0.6667,  1.3333/ -0.0906,  1.3333/ -0.6667,  1.2644/  0.7356,  1.2644/  0.3429,  1.1714/  0.7356,  1.1714/  0.3429,  0.2333/ -1.3435,  0.2333/ -1.7667, -0.2333/ -1.3435, -0.2333/ -1.7667, -0.1361/ -1.1944, -0.1361/ -1.4875, -0.5125/ -1.1944, -0.5125/ -1.4875, -0.5663/ -0.9938, -0.5663/ -1.1326, -0.8674/ -0.9938, -0.8674/ -1.1326, -1.6720/  0.2560, -1.6720/ -0.3039, -1.6961/  0.2560, -1.6961/ -0.3039, -1.6815/  0.2968, -1.6815/ -0.2968, -1.7032/  0.2968, -1.7032/ -0.2968, -1.4807/  0.5182, -1.4807/ -0.0145, -1.4818/  0.5182, -1.4818/ -0.0145} {
%   \draw[cyan] (\x-.02,\y-.02) -- (\x+.02,\y+.02); 
%   \draw[cyan] (\x-.02,\y+.02) -- (\x+.02,\y-.02);
%   }

>>>>

\journal{Computational Geometry: Theory and Applications}

@@

%% or include affiliations in footnotes:
\author{Rainer M. Schaich\fnref{akn}}
\ead{rainer.schaich@eng.ox.ac.uk}
\fntext[akn]{Supported by the EPSRC DTA and the Worcester College Martin Senior Scholarship}

\author{Mark Cannon\fnref{coa}}
\ead{mark.cannon@eng.ox.ac.uk}
\fntext[coa]{Corresponding author}

\address{Department of Engineering Science, University of Oxford, Oxford,  OX1 3PJ, UK}

@@

The induced graph~$G(P)$ of a polytope~$P$ is the graph with vertices and edges that coincide with the vertices and edges of the polytope itself~\cite{Bondy:2008}.
%
In this paper we only use one property of induced graphs, namely the \emph{Perles Conjecture}~\cite{Kalai:1988}:
\emph{For a simple polytope~$P$ the graph~$G(P)$ determines the combinatorial structure of~$P$.}

@@

Since $\mathcal W(p)$ is simple almost everywhere in~$Y$, i.e. each vertex is defined by exactly $n$ active inequalities, we have $\abs{\mathcal A_\kappa(p)}=n$ for all $p\in Y$ and all $\kappa$.

@@

The Perles Conjecture~\cite{Kalai:1988} states that the combinatorial structure of a simple polytope is uniquely determined by its graph, that is, as long as the induced graph of~$\mathcal W(p)$ remains unchanged so does its combinatorial structure.

@@

Let~$\mathcal C$ be a polyhedral complex such that in each $d$-dimensional element~$\mathcal P_j\in\mathcal C$ the set-valued map is given by $\mathcal W(p) = \{z\in\mathbb R^n:a_i z\leq b_{i,k_j} + c_{i,k_k} p\}$. 
%
It is worth pointing out that any such polyhedral complex is not assumed to be minimal, since the minimal such complex could have non-convex elements, those elements can however be partitioned such that every element of the non-minimal $\mathcal C$ are convex polyhedra. 
%
A natural way to obtain a convex polyhedral complex is by projecting the facets of the set
%
\begin{equation}
  E=\left\{(p,t_1,\dots,t_m)\in Y\times\mathbb R^{m}:\phi_i(p)\leq t_i\right\}
\end{equation}
%
onto $\mathbb R^d$.
%
The set of vertices of elements in the complex coincides with the union of all vertices of $d$-dimensional faces of $\epi(\phi_i)$ for all $i\in\{1,\dots,m\}$, i.e.
%
$$
	\bigcup_{P\in\mathcal C}\text{vert}(P) = \bigcup_{(\ast)} \text{vert}(\pi_d(F)) = \bigcup_{i\in\{1,\dots,m\}}\pi_d(\text{vert}(\epi(\phi_i))),
$$
%
with $(\ast) = \{F: F \text{ is a } d\text{-dimensional face of } \epi(d_i) \text{ for some } i\in\{1,\dots,m\}\}$.
%
It is now obvious that the graph $\mathscr G(\mathcal W\vert_{\mathcal P_j})$ on each $d$-dimensional element $\mathcal P_j\in\mathcal C$ is entirely defined by the values of $\mathcal W(p_j)$ at the vertices $p_j\in\text{vert}(\mathcal P_j)$.
%
In each~$\mathcal P_j$ we have $\mathcal W(p) = \{z: a_i z\leq \sum_f \lambda_f t_{i,j,f}, \sum_f\lambda_f p_{j,f}=p, \sum_f\lambda=1,{\bf{0}}\leq\lambda\leq{\bf{1}}\; \forall i\in\{1,\dots,m\}\}$
%
Therefore, if~$\mathcal A_\kappa\subset\{1,\dots,m\}$ such that~$\abs{\mathcal A_\kappa}=d$ and $a_\kappa v_\kappa = t_{\kappa,j}$ defines a vertex for $\mathcal W(p_j)$, then $a_\kappa v_\kappa = \sum_f \lambda_f t_{\kappa,f}$ defines a vertex for $\mathcal W(p)$.

@@

\begin{figure}
\centering
\begin{tikzpicture}[scale=2.5]
\draw[step=.5,gray,very thin] (-2,-2) grid (2,2);
\foreach \x in {-2,-1.5,...,2} \draw (\x,-2) node[below] {$\x$};
\foreach \y in {-2,-1.5,...,2} \draw (-2,\y) node[left] {$\y$};
\draw[-latex'] (-2,-2) -- (2.2,-2) node[below] {$x_1$};
\draw[-latex'] (-2,-2) -- (-2,2.2) node[left] {$x_2$};
\draw[blue,thick] ( -0.2333,   1.7667) -- ( -1.3333,   0.6667) -- ( -1.4807,   0.5182) -- ( -1.6815,   0.2968) -- ( -1.6720,   0.2560) -- ( -1.6039,   0.1353) -- ( -1.5073,  -0.0145) -- ( -1.0649,  -0.5786) -- ( -0.5663,  -1.1326) -- ( -0.1361,  -1.4875) -- (  0.2333,  -1.7667) -- (  1.3333,  -0.6667) -- (  1.4807,  -0.5182) -- (  1.6499,  -0.3316) -- (  1.5962,  -0.2075) -- (  1.5190,  -0.0928) -- (  1.4796,  -0.0407) -- (  1.1714,   0.3429) -- (  0.9224,   0.6499) -- (  0.1793,   1.4518) -- (  0.1361,   1.4875) -- ( -0.2333,   1.7667) -- cycle;
\draw[red] (  2.0000,   0.0000) -- (  0.0000,   2.0000) -- ( -2.0000,  -0.0000) -- ( -0.0000,  -2.0000) -- (  2.0000,   0.0000) -- cycle;
\foreach \x/\y in { -0.2333/  1.7667,  0.1361/  1.4875,  0.1793/  1.4518, -1.3333/  0.6667, -1.0649/ -0.5786, -1.5073/ -0.0145, -1.6039/  0.1353,  0.9224/  0.6499,  1.6499/ -0.3316,  1.4807/ -0.5182,  1.5962/ -0.2075,  1.4796/ -0.0407,  1.5190/ -0.0928,  1.3333/ -0.6667,  1.1714/  0.3429,  0.2333/ -1.7667, -0.1361/ -1.4875, -0.5663/ -1.1326, -1.6720/  0.2560, -1.6815/  0.2968, -1.4807/  0.5182} \draw[green!80!black] (\x,\y) circle (.75pt);
\foreach \x/\y in {  0.2160/  1.4706,  0.5125/  1.3332,  0.5456/  1.3134, -1.3333/  0.1741, -1.2021/ -0.7778, -1.5526/ -0.4386, -1.6336/ -0.3595,  1.0596/  0.9390,  1.6619/  0.2996,  1.4818/  0.0827,  1.6168/  0.3790,  1.5138/  0.4829,  1.5486/  0.4501,  1.3333/ -0.0915,  1.2515/  0.7356, -0.2160/ -1.3448, -0.5125/ -1.1956, -0.8500/ -1.1326, -1.6915/ -0.3039, -1.6976/ -0.2809, -1.4818/ -0.0094} \draw[yshift=-.5pt,xshift=-.5pt,magenta] (\x,\y) rectangle ++(1pt,1pt);
% \foreach \x/\y in {0.2333/  1.7667,  0.2333/  1.4511, -0.2333/  1.7667, -0.2333/  1.4511,  0.5125/  1.4875,  0.5125/  1.3157,  0.1361/  1.4875,  0.1361/  1.3157,  0.5482/  1.4518,  0.5482/  1.2973,  0.1793/  1.4518,  0.1793/  1.2973, -1.3333/  0.6667, -1.3333/  0.1672, -1.3333/  0.6667, -1.3333/  0.1672, -1.0649/ -0.5786, -1.0649/ -0.7979, -1.2021/ -0.5786, -1.2021/ -0.7979, -1.5073/ -0.0145, -1.5073/ -0.4386, -1.5614/ -0.0145, -1.5614/ -0.4386, -1.6039/  0.1353, -1.6039/ -0.3664, -1.6336/  0.1353, -1.6336/ -0.3664,  1.0596/  0.9404,  1.0596/  0.6499,  0.9224/  0.9404,  0.9224/  0.6499,  1.6684/  0.3316,  1.6684/ -0.3316,  1.6499/  0.3316,  1.6499/ -0.3316,  1.4818/  0.0948,  1.4818/ -0.5182,  1.4807/  0.0948,  1.4807/ -0.5182,  1.6210/  0.3790,  1.6210/ -0.2075,  1.5962/  0.3790,  1.5962/ -0.2075,  1.5171/  0.4829,  1.5171/ -0.0407,  1.4796/  0.4829,  1.4796/ -0.0407,  1.5486/  0.4514,  1.5486/ -0.0928,  1.5190/  0.4514,  1.5190/ -0.0928,  1.3333/ -0.0906,  1.3333/ -0.6667,  1.3333/ -0.0906,  1.3333/ -0.6667,  1.2644/  0.7356,  1.2644/  0.3429,  1.1714/  0.7356,  1.1714/  0.3429,  0.2333/ -1.3435,  0.2333/ -1.7667, -0.2333/ -1.3435, -0.2333/ -1.7667, -0.1361/ -1.1944, -0.1361/ -1.4875, -0.5125/ -1.1944, -0.5125/ -1.4875, -0.5663/ -0.9938, -0.5663/ -1.1326, -0.8674/ -0.9938, -0.8674/ -1.1326, -1.6720/  0.2560, -1.6720/ -0.3039, -1.6961/  0.2560, -1.6961/ -0.3039, -1.6815/  0.2968, -1.6815/ -0.2968, -1.7032/  0.2968, -1.7032/ -0.2968, -1.4807/  0.5182, -1.4807/ -0.0145, -1.4818/  0.5182, -1.4818/ -0.0145} {
%   \draw[cyan] (\x-.02,\y-.02) -- (\x+.02,\y+.02); 
%   \draw[cyan] (\x-.02,\y+.02) -- (\x+.02,\y-.02);
%   }
